\chapter{C++ Basics}

Topics:
\begin{itemize}
    \item Statements, Expressions, functions and libraries. Syntax Errors
    \item Comments. 4 reasons to write comments. Good comments
    \item Varaibles, definition. l-values and r-values. Initialization
    vs. Assignment. Undefined behaviour
    \item cout, endl, cin, output(<<) and input(>>) operators
    \item functions, return values and types, reusing functions,
    function call precedence over (<<), pointers to function names
    \item Functions
    \begin{itemize}
        \item function parameters and arguments, pass-by-value
        \item Usefulness of functions - Organization, reusability, testing, 
        extensibility, abstraction. Refactoring meaning
        \item Keywords and naming identifiers, good naming conventions
        \item Local scope
    \end{itemize}
    \item Literals, operands, operators -> unary, binary, and ternary
    \item Whitespaces, basic formatting. 6 rules to follow
    \item Forward declarations of functions. Declaration vs definition. ODR. Function prototypes.
    \item Multiple files for a single program.
    \begin{itemize}
        \item Naming conflicts, namespaces and the std namespace
    \end{itemize}
    \item Headers, their purposes. Header guards. Declaring vs defining
    functions in headers. Handling different directories. Best pracices.
    \item Preprocessors and Headers
    \begin{itemize}
        \item Preprocessors. Macro defines -> function defines and object defines
        Object defines with and without substitution text. Conditional compilation. Scope of defines -> Only within a single file.
        \item Header guards to remove duplicate definitions of functions. Limitations of header guards. Multiple declarations allowed, not 
        multiple definitions. \#pragma usage.
        \item 8 steps for designing any program. Some advice on writing programs
    \end{itemize}
    \item Syntax and semantic errors. Debugger. Stepping -> into, over, out. Run to cursor. Run/continue/go. Breakpoints.
    \item Comprehensive quiz on Chapter 1 concepts
\end{itemize}
